\sysfull

### 2018-08-03 paper/asplos19/coalescing.tex
restructure the paper directory
New HG figure inserted (and explained)

\begin{wrapfigure}{t}{0.3\textwidth}
\fbox{\parbox{\linewidth}{
	\captionof{algorithm}{Coalescing}
	\label{algo:genCoalescing}
	\scriptsize
	%\small
	%
	\begin{algorithmic}[1]
        \State $B \leftarrow $ \Call{$f_\text{reboot}$}{$x$}
        \State $H \gets 0$ 
        \While{$\texttt{true}$}       
	        \State $ i \gets 0$
	        %
	        \While{$ i <= B$}
		        \State \Call{execute\_task}{$T_\texttt{i}$}
		        \State $W \leftarrow $ \Call{$f_\text{weight}$}{$T_\text{i}$}
		        \State $i \gets i + W$
				\State $H \gets H + W$
	        \EndWhile
	        %
	        \State \Call{commit\_to\_fram}{\null}
	        \State $B \leftarrow $ \Call{$f_\text{commit}$}{$B$}
        \EndWhile
	\end{algorithmic}}}
\end{wrapfigure}
%	\begin{subfigure}[t]{\linewidth}
%	\end{subfigure}
%
%

@@

\begin{wrapfigure}{t!}{0.3\textwidth}
	\centering
	\includegraphics[width=0.3\columnwidth]{figures/slowCoal}
	\caption{The {\em energy-oblivious coalescing} algorithm \emph{linearly} updates its coalescing target.}
	\label{fig:energyBlind}
\end{wrapfigure}

@@

@@

\begin{wrapfigure}{}{0.5\textwidth}
	\centering
	\includegraphics[width=0.5\columnwidth]{figures/energy-aware-coal.pdf}
	\caption{The {\em history-guided coalescing} algorithm uses its recent history of execution to estimate the available amount of energy and set the coalescing target accordingly.}
	\label{fig:energyAware}
\end{wrapfigure}

@@

Figure~\ref{fig:energyAware} illustrates the operation of the history-guided
coalescing strategy.  Each white box is a task and each red box is a commit.
Time goes left to right and consecutive white boxes with no intervening commit
are coalesced tasks.  A gray box is a task interrupted by a power failure.  At
the top, the figure shows the $i$th execution period, which has a history
value of $H^{(i)} = 4$.  $B$ is initially two and decreases to one.  Once the
value of $B$ reaches one, HG is, in effect, expecting a power failure,
justifying the decrease in the coalescing target.  After the power failure, HG
first updates the history $H = H^{i+1} = 8$. HG then uses the value of $H$ to
update $B$, setting $B$ equal to four and continuing execution.

>>>>

% \begin{wrapfigure}{t}{0.3\textwidth}
\begin{figure}{t}
\fbox{\parbox{\linewidth}{
	\captionof{algorithm}{Coalescing}
	\label{algo:genCoalescing}
	\scriptsize
	%\small
	%
	\begin{algorithmic}[1]
        \State $B \leftarrow $ \Call{$f_\text{reboot}$}{$z$}
        \State $H \gets 0$ 
        \While{$\texttt{true}$}       
	        \State $ i \gets 0$
	        %
	        \While{$ i <= B$}
		        \State \Call{execute\_task}{$T_\texttt{i}$}
		        \State $W \leftarrow $ \Call{$f_\text{weight}$}{$T_\text{i}$}
		        \State $i \gets i + W$
				\State $H \gets H + W$
	        \EndWhile
	        %
	        \State \Call{commit\_to\_fram}{\null}
	        \State $B \leftarrow $ \Call{$f_\text{commit}$}{$B$}
        \EndWhile
	\end{algorithmic}}}
% \end{wrapfigure}
\end{figure}

%	\begin{subfigure}[t]{\linewidth}
%	\end{subfigure}
%
%

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.49\columnwidth}
        \includegraphics[width=\columnwidth]{figures/slowCoal}
		\caption{The {\em energy-oblivious coalescing} algorithm \emph{linearly} updates its coalescing target.}
		\label{fig:energyBlind}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\columnwidth}
       	\includegraphics[width=\columnwidth]{figures/energy-aware-coal.pdf}
		\caption{The {\em history-guided coalescing} algorithm uses its recent history of execution to estimate the available amount of energy and set the coalescing target accordingly.}
		\label{fig:energyAware}
    \end{subfigure}
    % \caption{Pictures of animals}\label{fig:animals}
\end{figure}

% % \begin{wrapfigure}{t!}{0.3\textwidth}
% \begin{figure}
% 	\centering
% 	\includegraphics[width=0.48\columnwidth]{figures/slowCoal}
% 	\caption{The {\em energy-oblivious coalescing} algorithm \emph{linearly} updates its coalescing target.}
% 	\label{fig:energyBlind}
% % \end{wrapfigure}
% \end{figure}

% % \begin{wrapfigure}{}{0.5\textwidth}
% \begin{figure}
% 	\centering
% 	\includegraphics[width=0.48\columnwidth]{figures/energy-aware-coal.pdf}
% 	\caption{The {\em history-guided coalescing} algorithm uses its recent history of execution to estimate the available amount of energy and set the coalescing target accordingly.}
% 	\label{fig:energyAware}
% % \end{wrapfigure}
% \end{figure}

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{figures/hg-coal-horiz.pdf}
    \caption{HG coalescing sample execution across two power cycles.}
    \label{fig:hg-coal}
\end{figure*}

@@

@@

Figure~\ref{fig:hg-coal} illustrates the operation of the history-guided
coalescing strategy.
The figure shows two power cycles following the $i$th, the latter having an
execution history $H^{(i)} = 4$.
Based on that, $B$ is initially set to two and then decreases to one. Once the
value of $B$ reaches one, HG is, in effect, expecting a power failure,
justifying the conservative approach. After the power failure, HG
uses the most recent history $H^{(i+1)} = 8$ to set $B = 4$
and continue execution.
